Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-03-10 demystify.tex
mend
add cover page

    % Title
    \node[align=center] at ($(current page.center)+(0,-5)$) 
    {
    {\fontsize{28}{28} \selectfont {{Demystifying the Computer Science}}} \\[0.15in]
    {\fontsize{28}{28} \selectfont {{PhD Admission in the US}}} \\[0.2in]    
    {\fontsize{18}{18} \selectfont {{A Handbook for International \emph{and Domestic} Students}}} \\[0.5in]

>>>>

    % Title
    \node[align=center] at ($(current page.center)+(0,-5)$) 
    {
    {\fontsize{24}{24} \selectfont {{Demystifying the Computer Science}}} \\[0.15in]
    {\fontsize{24}{24} \selectfont {{PhD Admission in the US}}} \\[0.2in]    
    {\fontsize{18}{18} \selectfont {{A Handbook for International \emph{and Domestic} Students}}} \\[0.5in]
